A note on $\K$ of Kac---Moody groups over a field

### 2017-08-16 paper.tex
Minor

Now set $s:= t_{32}(1)$, $t:= t_{32}(-1) \in \SL(3, \ZZ)$ and consider the decomposition 
$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
Now application of Westaway's criterion to the matrix $sq$ gives incorrect answer.
More precisely, it incorrectly determines the parity of the third column of $d$ to be even rather than odd.
\end{example}

>>>>

Now set $s:= t_{32}(1)$, $t:= t_{32}(-1) \in \SL(3, \ZZ)$ and consider the decomposition 
$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
Now application of Westaway's criterion to the matrix $sq$ incorrectly determines the parity of the third column of $t^{-1}ds^{-1}=d$ to be even rather than odd.
\end{example}
